Technical Report

### 2024-03-04 Reports/tech_report1.tex
update report

>>>>

\section{March 4}

\subsection{Compute gamma for layer 7 for normal 5x100, pure y-constraints, with 0.25}

This experiment is to compute the gamma of layer 7 normal 5x100 with pure-y constraints constraints, with open 47 node.

The running code's file name is \verb*|DiamondLipschitz_V0p7_test.py|. And the partial output file name is \verb*|DL_V0p3_layer7_comparison_layerWeight_0p25.txt|.  It is based on the new pure y-constraints, use MILP model to compute the gamma of layer 7 with open 81 ReLU.

\begin{itemize}
	\item\emph{Experiments Id}: 030400102024

The same as previous experiments, except that when choosing open ReLU nodes in layer 3 and 5, we adjust the coefficient from 0.5 to 0.25.

\begin{itemize}
	\item \emph{Log:} \verb*|DL_V0p3_layer7_comparison_layerWeight_0p25.txt|.

	\item \emph{Total time:} 36546s.

	\item \emph{Key results:}  The average gamma of this layer is:  2.7275173326094007

	The average solution for gamma of this layer is:  2.6553045443329144

	\item  \emph{Binary output}: The gamma of layer 7 is stored in the file \verb*|Diamond_record_6_100_dictionary_with_end_layer7_2024_03_02_11_26_32.b|.

\subsection*{Find compensating values for 6x500}

For 6x500 normal, we have:

layer 3:  0.016880075 0.002558308045652896.

layer 5:  0.012260569 0.0025547753866600885.

layer 7:  0.009393309 0.0024678166341261.

layer 9:  0.01012707 0.002454717660170578.

For 6x500 PGD 0.3:

layer 3:  0.07386457 0.0007851583929458109

layer 5:  0.16980232 0.006956658962832778

layer 7:  0.061593153 0.007807677391123027

layer 9:  0.06259781 0.007048364295146268

For 6x500 PGD 0.1:

0.059109613 0.0024193087092992493

0.023277795 0.004074500587174903

0.031013045 0.003997824062301744

0.020129312 0.0031846138593207844
